### 2015-02-22 fundamentals/impl.tex
cleaned up interchange ex

\gls{ABM} is inherently object-oriented because agents represent
discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator
creates a set of classes on which agent plug-ins
are based. In addition, a set of tools are also provided to enrich the
\gls{API} and supply a robust suite of behaviors for the developer.
Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For
example, agents rely on a paradigm of dynamic loading and clean plug-in
behavior at the start of the simulation. They also use the resource exchange
paradigm \gls{API} for trading resources with one another.

>>>>

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based. In addition, a set of tools
are also provided to enrich the \gls{API} and supply a robust suite of behaviors
for the developer.  Agent plug-ins utilize the generic core \gls{API} to
interact with one another.  For example, they use the resource exchange paradigm
\gls{API} for trading resources with one another.
